Supplementary Information

### 2020-08-26 doc/manuscript/MEE_manuscript.Rmd
add Table S4
#42

*List not yet complete. Current list includes all those who have contributed tree-ring data and/or intellectually, but all not site PIs.*

*other contributors may move up in the list if they contribute a lot*

@@

We analyzed previously collected tree-ring data from ten sites ranging from 9.15$^\circ$ to 61.30$^\circ$ N latitude and representing a wide range of forest and tree types: tropical broadleaf deciduous and evergreen, temperate broadleaf deciduous and needleleaf evergreen, and boreal needleleaf evergreen (Tables 1, S1-S2).
Nine of these sites (exception: LT) are large forest dynamics plots of the Forest Global Earth Observatory [ForestGEO; @anderson-teixeira_ctfs-forestgeo:_2015].
Trees of species represented within the ForestGEO plots were cored within the plot (n=#) and/or in the vicinity (n=#; max distance: # km), following a variety of sampling protocols designed to meet the varied objectives of the original studies (Table 1). 
In using this variety of data sources, we ensured that our approach was able to handle a variety of challenges presented by varying methodologies and forest types.

@@

**Interactive effects of $DBH$ and climate were found for #% of species-variable combinations**.

>>>>

@@

We analyzed previously collected tree-ring data from ten sites ranging from 9.15$^\circ$ to 61.30$^\circ$ N latitude and representing a wide range of forest and tree types: tropical broadleaf deciduous and evergreen, temperate broadleaf deciduous and needleleaf evergreen, and boreal needleleaf evergreen (Tables 1, S1-S2).
Nine of these sites (exception: LT) are large forest dynamics plots of the Forest Global Earth Observatory [ForestGEO; @anderson-teixeira_ctfs-forestgeo:_2015].
Trees of species represented within the ForestGEO plots were cored within the plot (n=#) and/or in the vicinity (n=#; max distance: # km), following a variety of sampling protocols designed to meet the varied objectives of the original studies (Table S1). 
In using this variety of data sources, we ensured that our approach was able to handle a variety of challenges presented by varying methodologies and forest types.

@@

**Interactive effects of $DBH$ and climate were found for #% of species-variable combinations**. 
*(some details)* (Table S4).

### 2020-08-26 doc/manuscript/MEE_manuscript_SI.Rmd
add Table S4
#42

\newpage
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table_raw <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climate_interactions_summary.csv", stringsAsFactors = FALSE, check.names = FALSE)
#this reads in the table, but knit fails if I try to render it (probably because of underscores). It also needs ot be rearranged
#kable(table_raw, format = "latex", booktabs = TRUE, caption = "Table S  . Frequency of DBH-climate interactions", escape = F)%>%
#  kable_styling(latex_options = c("scale_down", "hold_position")) 
```

>>>>

\newpage
## Table S4. Frequency of $DBH$-climate interactions across all sites and growth metrics
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table_raw <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climate_interactions_summary.csv", stringsAsFactors = FALSE, check.names = FALSE)
#this reads in the table, but knit fails if I try to render it (probably because of underscores). It also needs ot be rearranged
#kable(table_raw, format = "latex", booktabs = TRUE, caption = "Table S  . Frequency of DBH-climate interactions", escape = F)%>%
#  kable_styling(latex_options = c("scale_down", "hold_position")) 
```
